%-------------------------
% Author : Mohsin Mumtaz
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Mohsin Mumtaz} & Email : \href{mailto:}{mohsinmumtaz21@gmail.com}\\
   \href{https://github.com/immohsin}{\underline{Github}} 
   \href{https://www.linkedin.com/in/mohsin-mumtaz-680915ab}{\underline{LinkedIn}}  
   \href{https://medium.com/@im_mohsin}{\underline{Medium}} 
   \href{https://immohsin.hashnode.dev/}{\underline{Hashnode}} & Mobile : +91 9738226982
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Slanglabs}{Bangalore}
      {Senior Software Engineer}{Sept 2021 - Present}
      \resumeItemListStart
        \resumeItem{Web SDK}
         {Lead Web SDK product development and road map. During this period there was 2x improvement in customer integration and end user adoption.}
        \resumeItem{NLU Intent Processor}
         {Built new way of processing intent on Slanglabs web SDK. This provided flexibility to handle entity resolution independently by apps.}
        \resumeItem{Built new Domains}
         {Designed and implemented the new domain for web assistant sdk in tight deadline. It helped us secure POC and subsequent integration opportunity with large financial institution.}
        \resumeItem{Conva Backend Platform}
         {Designed and Implemented API's for Slanglabs new Conva platform. Conva significantly reduced turnaround time  in building, managing and integrating voice assistant.}
        \resumeItem{Notification system for NLU assistant training}
         {Implemented SSE using google pubsub to notify assistant training status to console.}
        \resumeItem{SKU Upload}
         {Designed and Implemented support for uploading large SKU data for assistant training. This resulted is over \textbf{50\%} improvement in page loads }
      \resumeItemListEnd

    \resumeSubheading
      {Slanglabs}{Bangalore}
      {Software Engineer}{Sept 2018 - Sept 2021}
      \resumeItemListStart
        \resumeItem{Cache \href{https://www.slanglabs.in/blog/layer-your-cache-system-like-a-wedding-cake}{\underline{(blog link)}}}
          {Built Multi level cache to improve slang core inference performance by almost \textbf{25\%}.}
        \resumeItem{Analytics Microservice}
         {Built and scaled analytic ingestion pipeline to handle peak traffic.}
        \resumeItem{Database}
          {Designed and Implemented postgress database for slang micro services from the flat files that ever earlier used to store data and performed optimization to handle concurrent requests.}
        \resumeItem{Magento 2 Extension }
          {Implemented Magneto 2 extension that enable developers to add Slanglabs voice assistant to any online store with zero code implementation.}
        \resumeItem{E2E testing infra}
          {Built entire e2e testing infra using Cypress for slang console which contributed to quicker release cycle.}
      \resumeItemListEnd


    \resumeSubheading
      {Doselect}{Bangalore}
      {Software Engineering Intern}{Jan 2018 - August 2018}
      \resumeItemListStart
        \resumeItem{Infrastructure tool}
          {Service to run deployments and metrics generations. Involved in building the tool from scratch and building utilities for effiecient report generation. Implemented asynchronous tasks using celery and RabbitMq.}
        \resumeItem{RestFul API}
          {Built API to get solution revisions of the problems used by partner companies, built using tastypie framework. The feature is live and in production.}
        \resumeItem{Mail Notifications}
          {Built feature for platform users to receive periodic email notification about users activity.}
        \resumeItem{User Management API}
          {Core service for managing the user and user permissions from easy to use dashboard.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, Golang, Javascript, Java}
     }
    \item{
      \textbf{Technologies}{: AWS, GCP, Firebase, Web Development, Docker, CircleCi}
    }
    \item{
      \textbf{Libraries and Framework}{: Tornado, Django, Flask, Celery}
    }
  \resumeSubHeadingListEnd
 
 
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Ramaiah Institute Of Technology}{Bangalore,}
        {Master of Computer Application;  CGPA: 8.35}{July. 2018}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeSubItem{Speech Recognition \href{https://medium.com/@im_mohsin/speech-to-text-in-python-c344725b55a9}{\underline{(blog link)}}}
      {A Speech to Text web application developed using python/django that  performs streaming and non-streaming services.}
    \resumeSubItem{Offline/Online indicator service}
      {Building a simple service which notifies if a user is offline/online during chat. The service is load balanced using nginx and stores user status in redis.}
    \resumeSubItem{Vehicle Tracking System}
      {Arduino device to track vehicle with complete gps sensors and store location data in google firebase for access through web and mobile app interface.}
    \resumeSubItem{Image Management API}
      {Rest API with GET, POST, PATCH request methods to save and retrieve images from the local file system stored by the API service. Developed using Python and Django Rest Framework.}
  \resumeSubHeadingListEnd


%-----------Awards & Extra Curricular-----------------
\section{Awards and Extra Curricular}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Recognition for building productivity tool}{Slanglabs}
        {Built a docker-compose tool that helps developer run entire slanglabs tech stack with a single command.}{Jan 2021}
    \resumeSubheading
        {2nd Place in Payse Hackathon}{Nucleus Software}
        {Won online hackathon sponsored by nucleus software to find loopholes in their payment system.}{March 2019}
  \resumeSubHeadingListEnd

\end{document}
